Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-10-15 grove-paper.tex
Partially fix vertex and edge data in figures

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "\vChangeZ" [> "\eChangeZ"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}}
\label{fig:Editing Different Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}}
\label{fig:Editing Different Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Different Parts of the Code-a} with \autoref{fig:Editing Different Parts of the Code-b}}
\label{fig:Editing Different Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code}
\label{fig:Editing Different Parts of the Code}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}}
\label{fig:Editing Nested Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}}
\label{fig:Editing Nested Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}}
\label{fig:Editing Nested Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code}
\label{fig:Editing Nested Parts of the Code}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{24}$" [> "R$_{23}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   "$\texttt{y}_{26}$" [> "R$_{25}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{24}$" [> "R$_{23}$"],
    "$\texttt{y}_{26}$" [> "R$_{25}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
TODO: UI (at least moc up)
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{w}_{20}$" [> "R$_{27}$"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'],
   "$\texttt{w}_{20}$" [> "R$_{29}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{\vWrapPlus} [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    {},
    b/"$\texttt{w}_{20}$" [> "R$_{27}$"']
   },
   {}
  }
 },
};
\path [edge style,->] (a) to ["R$_{29}$",out=-60,in=60] (b);
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"] -> {
   v2/"\vSimpleTimes" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{w}_{20}$" [> "R$_{27}$"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code TODO: move to previous figure}
\label{fig:Multi-parent-e}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure*}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"'] -> {
   v2/"\vSimpleTimes" [> "L$_{21}$"'] -> {
    {},
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by copy as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"'] -> {
   v2/"\vSimpleTimes" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{+}_{32}$" [> "R$_{31}$"] -> {
     "$\texttt{*}_{34}$" [> "L$_{33}$"'] -> {
      {},
      {}
     },
     {}
    }
   },
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by copy as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"] -> {
   v2/"\vSimpleTimes" [> "L$_{21}$"'],
   {}
  }
 }
};
\path[edge style,->] (v2) to ["R$_{31}$",out=-60,in=-60] (v8);
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by reference as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Single-User Cycles}
\label{fig:Single-User Cycles}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{+}_{34}$" [> "L$_{33}$"'],
    "$\texttt{*}_{36}$" [> "R$_{35}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'] -> {
   },
   {
    "$\texttt{+}_{34}$" [> "R$_{37}$"] -> {
     "$\texttt{*}_{36}$" [> "L$_{39}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'] -> {
   },
   {
    "$\texttt{*}_{36}$" [> "R$_{41}$"] -> {
     "$\texttt{+}_{34}$" [> "L$_{43}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'] -> {
   },
   {
    v1/"$\texttt{+}_{34}$" [> "R$_{37}$"],
    v2/"$\texttt{*}_{36}$" [> "R$_{41}$"]
   }
  }
 }
};
\path[edge style,->] (v1) to ["L$_{39}$",out=-45,in=-135] (v2);
\path[edge style,->] (v2) to ["L$_{43}$",out=-90,in=-90] (v1);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-User Cycles}
\label{fig:Multi-User Cycles}
\end{figure*}

>>>>

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{DifferentAlice}{L}
\newvertex{DifferentAlice}{u}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vChangeZ" [> "\eChangeZ"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}}
\label{fig:Editing Different Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{DifferentBob}{R}
\newvertex{DifferentBob}{v}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}}
\label{fig:Editing Different Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Different Parts of the Code-a} with \autoref{fig:Editing Different Parts of the Code-b}}
\label{fig:Editing Different Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code}
\label{fig:Editing Different Parts of the Code}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{NestedAlice}{L}
\newvertex{NestedAlice}{w}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "\eMoveTimes"] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}}
\label{fig:Editing Nested Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{NestedBob}{L}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vDifferentAlice" [> "\eDifferentAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}}
\label{fig:Editing Nested Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}}
\label{fig:Editing Nested Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code}
\label{fig:Editing Nested Parts of the Code}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\newedge{MultiChildAlice}{R}
\newvertex{MultiChildAlice}{x}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {
    "\vMultiChildAlice" [> "\eMultiChildAlice"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\newedge{MultiChildBob}{R}
\newvertex{MultiChildBob}{y}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   "\vMultiChildBob" [> "\eMultiChildBob"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {
    "\vMultiChildAlice" [> "\eMultiChildAlice"],
    "\vMultiChildBob" [> "\eMultiChildBob"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
TODO: UI (at least moc up)
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\newedge{MultiParentAlice}{R}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vNestedAlice" [> "\eMultiParentAlice"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\newedge{MultiParentBob}{R}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'],
   "\vNestedAlice" [> "\eMultiParentBob"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{\vWrapPlus} [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    b/"\vNestedAlice" [> "\eMultiParentAlice"']
   },
   {}
  }
 },
};
\path [edge style,->] (a) to ["\eMultiParentBob",out=-60,in=60] (b);
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"] -> {
   v2/"\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vNestedAlice" [> "\eMultiParentAlice"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code TODO: move to previous figure}
\label{fig:Multi-parent-e}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure*}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"'] -> {
   v2/"\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by copy as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{SingleCyclePlus}{R}
\newvertex{SingleCyclePlus}{+}
\newedge{SingleCycleTimes}{L}
\newvertex{SingleCycleTimes}{*}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"'] -> {
   v2/"\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vSingleCyclePlus" [> "\eSingleCyclePlus"] -> {
     "\vSingleCycleTimes" [> "\eSingleCycleTimes"'] -> {
      {},
      {}
     },
     {}
    }
   },
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by copy as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{SingleCycleCycle}{R}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"] -> {
   v2/"\vSimpleTimes" [> "\eNestedBob"'],
   {}
  }
 }
};
\path[edge style,->] (v2) to ["\eSingleCycleCycle",out=-60,in=-60] (v8);
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by reference as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Single-User Cycles}
\label{fig:Single-User Cycles}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "$\texttt{+}_{34}$" [> "L$_{33}$"'],
    "$\texttt{*}_{36}$" [> "R$_{35}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
   },
   {
    "$\texttt{+}_{34}$" [> "R$_{37}$"] -> {
     "$\texttt{*}_{36}$" [> "L$_{39}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
   },
   {
    "$\texttt{*}_{36}$" [> "R$_{41}$"] -> {
     "$\texttt{+}_{34}$" [> "L$_{43}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
   },
   {
    v1/"$\texttt{+}_{34}$" [> "R$_{37}$"],
    v2/"$\texttt{*}_{36}$" [> "R$_{41}$"]
   }
  }
 }
};
\path[edge style,->] (v1) to ["L$_{39}$",out=-45,in=-135] (v2);
\path[edge style,->] (v2) to ["L$_{43}$",out=-90,in=-90] (v1);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-User Cycles}
\label{fig:Multi-User Cycles}
\end{figure*}
